UniScatter: Unifying\\Backscatter Communications, Symbiotic Radio, and Reconfigurable Intelligent Surface

### 2022-08-05 main.tex
:pencil: Update introduction

	This motivated \cite{Long2020a,Ding2020,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Yang2018,Han2021,Zhang2022,Xu2020b,Hua2022} to decode the primary link, perform \gls{sic}, then decode the backscatter link.

@@

	On the other hand, \gls{ris} is a promising technology that evolves wireless propagation environment using numerous passive reflecting elements (e.g., scattering antenna or programmable metamaterial) with adjustable amplitudes and/or phases \cite{Wu2021b}.
	% The scattered/reflected signals contain no additional information, but adds constructively (or destructively) with the direct component to enhance desired link (or suppress interference).
	The scattered signals contain no additional information, but adds constructively or destructively with the direct component to enhance desired signal or suppress interference, improving spectrum and energy efficiency.
	% Specifically, different IRS reflec- tion coefficients are set for different time slots in each channel coherence block to enable more flexible reflection design with generally less number of users selected to be served at each time slot, thus leading to a higher passive beamforming gain
	% Extensive research has been devoted to optimizing \gls{ris} phase shifts to improve communication, sensing, and power performances.
	Compared with backscatter nodes of \gls{bc} and \gls{sr}, the reflection pattern of \gls{ris} elements are deterministic and priorly known at transmitter and receiver.
	It motivated the use of fixed reflection pattern during each channel block to improve communication, sensing, and power performances \cite{Wu2018,Zhang2019a,Lin2022,Liu2022,Feng2022,Zhao2022}.
	% To create artificial diversity and enable flexible resource allocation, the concept of dynamic passive beamforming was first proposed for \gls{ofdm} systems \cite{Yang2020},
	% The concept of dynamic passive beamforming that chooses \gls{ris} reflection coefficients independently over different time slots within each channel block was first proposed for \gls{ofdm} systems \cite{Yang2020}, then extended to multi-user \gls{wpt} \cite{Qiu2022} and \gls{wpcn} \cite{Wu2021d,Hua2022a} with dedicated downlink power and uplink information phases.
	% The concept of dynamic passive beamforming, namely choosing \gls{ris} reflection coefficients independently over different time slots within each channel block, was first proposed for \gls{ofdm} systems \cite{Yang2020}, then extended to multi-user \gls{wpt} \cite{Qiu2022} and \gls{wpcn} \cite{Wu2021d,Hua2022a} with dedicated downlink power and uplink information phases.
	The concept of dynamic \gls{ris}, namely choosing independent reflection coefficients for different time slots within channel block, was first proposed to assist \gls{ofdm} systems \cite{Yang2020}, then extended for the downlink power and uplink information phases of \gls{wpcn} \cite{Wu2021,Wu2021d,Hua2022a}.
	Dynamic \gls{ris} introduced artificial channel diversity and flexible resource allocation, but missed the opportunity to encode its own message.
	% Interestingly, \cite{Karasik2020} reported from information-theoretic perspective that if
	From an information-theoretic perspective, \cite{Karasik2020} reported using \gls{ris} as an auxiliary equipment to maximize the \gls{snr} is generally rate-suboptimal for finite input constellations.
	% From an information-theoretic perspective, \cite{Karasik2020} reported using \gls{ris} as a pure auxiliary device to maximize the \gls{snr} at the receiver is generally rate-suboptimal for finite input constellations.
	% The capacity-achieving transmission scheme is to joint
	Instead, joint transmitter-\gls{ris} encoding achieves the capacity of \gls{ris}-aided channel, while layered encoding with \gls{sic} decoding (i.e., \gls{sic}-based \gls{sr}) can outperform pure passive beamforming at high \gls{snr}.
	Further attempts

	How to combine backscatter modulation and passive beamforming

>>>>

	This motivated \cite{Long2020a,Ding2020,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Yang2018,Han2021,Zhang2022} to decode the primary link, perform \gls{sic}, then decode the backscatter link.

@@

	On the other hand, \gls{ris} is a promising technology that evolves wireless propagation environment using numerous passive reflecting elements (e.g., scattering antenna or programmable metamaterial) with adjustable amplitudes and/or phases \cite{Wu2021b}.
	% The scattered/reflected signals contain no additional information, but adds constructively (or destructively) with the direct component to enhance desired link (or suppress interference).
	% The scattered signals contain no additional information, but adds constructively or destructively with the direct component to enhance desired signal or suppress interference, improving spectrum and energy efficiency.
	The scattered signals contain no additional information, but adds constructively or destructively with the direct component to enhance desired signal or suppress interference.
	% Specifically, different IRS reflec- tion coefficients are set for different time slots in each channel coherence block to enable more flexible reflection design with generally less number of users selected to be served at each time slot, thus leading to a higher passive beamforming gain
	% Extensive research has been devoted to optimizing \gls{ris} phase shifts to improve communication, sensing, and power performances.
	Compared with backscatter nodes of \gls{bc} and \gls{sr}, the reflection pattern of \gls{ris} elements are deterministic and priorly known at transmitter and receiver.
	It motivated the use of fixed reflection pattern during each channel block to improve communication, sensing, and power performances \cite{Wu2018,Zhang2019a,Lin2022,Liu2022,Feng2022,Zhao2022}.
	% To create artificial diversity and enable flexible resource allocation, the concept of dynamic passive beamforming was first proposed for \gls{ofdm} systems \cite{Yang2020},
	% The concept of dynamic passive beamforming that chooses \gls{ris} reflection coefficients independently over different time slots within each channel block was first proposed for \gls{ofdm} systems \cite{Yang2020}, then extended to multi-user \gls{wpt} \cite{Qiu2022} and \gls{wpcn} \cite{Wu2021d,Hua2022a} with dedicated downlink power and uplink information phases.
	% The concept of dynamic passive beamforming, namely choosing \gls{ris} reflection coefficients independently over different time slots within each channel block, was first proposed for \gls{ofdm} systems \cite{Yang2020}, then extended to multi-user \gls{wpt} \cite{Qiu2022} and \gls{wpcn} \cite{Wu2021d,Hua2022a} with dedicated downlink power and uplink information phases.
	% The concept of dynamic \gls{ris}, namely choosing independent reflection coefficients for different time slots within channel block, was first proposed to assist \gls{ofdm} systems \cite{Yang2020}, then extended for the downlink power and uplink information phases of \gls{wpcn} \cite{Wu2021,Wu2021d,Hua2022a}.
	The concept of dynamic \gls{ris}, namely choosing independent reflection coefficients over different time slots within channel block, was first considered for resource blocks of \gls{ofdm} systems, then extended to power and information phases of \gls{wpcn} \cite{Wu2021,Wu2021d,Hua2022a}.
	Dynamic \gls{ris} provided artificial channel diversity and flexible resource allocation, but missed the opportunity to encode its own message.
	% Interestingly, \cite{Karasik2020} reported from information-theoretic perspective that if
	From an information-theoretic perspective, \cite{Karasik2020} reported using \gls{ris} as an auxiliary equipment to maximize the \gls{snr} is generally rate-suboptimal for finite input constellations.
	% From an information-theoretic perspective, \cite{Karasik2020} reported using \gls{ris} as a pure auxiliary device to maximize the \gls{snr} at the receiver is generally rate-suboptimal for finite input constellations.
	% The capacity-achieving transmission scheme is to joint
	Instead, joint transmitter-\gls{ris} encoding achieves the capacity of \gls{ris}-aided channel, and layered encoding with \gls{sic} decoding (i.e., \gls{sic}-based \gls{sr}) can outperform pure passive beamforming at high \gls{snr}.
	It inspired \cite{Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hu2021b,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a} to employ \gls{ris} as an information source that combines passive beamforming and backscatter modulation in the overall reflection pattern.
	% In particular, \emph{overlay modulation} decouples the overall reflection pattern as the product of an information-bearing symbol and an auxiliary coefficient matrix.
	% In particular, \emph{overlay modulation} superposes information-bearing symbols over a common auxiliary matrix \cite{Xu2020b,Zhang2021d,Hu2021b,Hua2022}, \emph{spatial modulation} designs the reflection coefficients to maximize the \gls{snr} of different
	% In particular, \emph{overlay modulation} superposes information-bearing symbols over a common auxiliary matrix \cite{Xu2020b,Zhang2021d,Hu2021b,Hua2022}, \emph{spatial modulation} varies \gls{ris} reflection coefficients to maximize the \gls{snr} at different receive antennas \cite{Basar2020,Ma2020a,Yuan2021}, \emph{index modulation} divided the \gls{ris} into reflection and information elements, and evaluated the error performance of non-coherent backscatter detection.
	% In particular, \emph{overlay modulation} superposes information-bearing symbols over a common auxiliary matrix \cite{Xu2020b,Zhang2021d,Hu2021b,Hua2022}, \emph{spatial modulation} varies \gls{ris} reflection coefficients to maximize the \gls{snr} at different receive antennas \cite{Basar2020,Ma2020a,Yuan2021}, \emph{index modulation} divided the \gls{ris} into reflection elements for passive beamforming and information elements
	% In particular, \emph{overlay modulation} superposes information-bearing symbols over a common auxiliary matrix \cite{Xu2020b,Zhang2021d,Hu2021b,Hua2022}, \emph{spatial modulation} switches between reflection coefficient sets that maximize \gls{snr} at different receive antennas \cite{Basar2020,Ma2020a,Yuan2021}, \emph{index modulation} divides \gls{ris} into reflection elements for passive beamforming and information elements for on-off keying modulation \cite{Hu2021a}, and \emph{symbol level precoding} designs the reflection coefficients to
	% In particular, \emph{overlay modulation} superposes information-bearing symbols over a common auxiliary matrix \cite{Xu2020b,Zhang2021d,Hu2021b,Hua2022}, \emph{spatial modulation} switches between reflection coefficient sets that maximize \gls{snr} at different receive antennas \cite{Basar2020,Ma2020a,Yuan2021}, \emph{index modulation} divides \gls{ris} into reflection elements for passive beamforming and information elements for on-off modulation \cite{Hu2021a}, and \emph{symbol level precoding} creates a mapping from reflection coefficients to backscatter symbol \cite{Liu2019d,Bereyhi2020} where .
	% In particular, \emph{overlay modulation} superposes information-bearing symbols over a common auxiliary matrix \cite{Xu2020b,Zhang2021d,Hu2021b,Hua2022}, \emph{spatial modulation} switches between reflection coefficient sets that maximize \gls{snr} at different receive antennas \cite{Basar2020,Ma2020a,Yuan2021}, \emph{index modulation} divides \gls{ris} into reflection elements for passive beamforming and information elements for on-off modulation \cite{Hu2021a}, and \emph{symbol level precoding} maps reflection coefficients to backscatter symbols and optimizes to improve detection performance.
	% In particular, \emph{overlay modulation} superposes information-bearing symbols over a common auxiliary matrix \cite{Xu2020b,Zhang2021d,Hu2021b,Hua2022}, \emph{spatial modulation} switches between reflection coefficient sets that maximize \gls{snr} at different receive antennas \cite{Basar2020,Ma2020a,Yuan2021}, \emph{index modulation} divides \gls{ris} into reflection elements for passive beamforming and information elements for on-off modulation \cite{Hu2021a}, and \emph{symbol level precoding} maps reflection coefficients to backscatter symbols and optimizes for detection performance.
	% In particular, \emph{symbol level precoding} maps optimized \gls{ris} coefficient sets to backscatter symbols to improve detection performance,
	% In particular, \emph{symbol level precoding} maps \gls{ris} coefficient sets to backscatter symbols and optimizes for detection performance,
	% In particular, \emph{symbol level precoding} maps optimized \gls{ris} coefficient sets to backscatter symbols \cite{Liu2019d,Bereyhi2020}, \emph{overlay modulation} superposes information-bearing symbols over a common auxiliary matrix \cite{Xu2020b,Zhang2021d,Hu2021b,Hua2022}, \emph{spatial modulation} switches between reflection coefficient sets that maximize \gls{snr} at different receive antennas \cite{Basar2020,Ma2020a,Yuan2021}, and \emph{index modulation} divides \gls{ris} into reflection elements for passive beamforming and information elements for on-off modulation \cite{Hu2021a}.
	In particular, \emph{symbol level precoding} maps backscatter symbols to optimized \gls{ris} coefficient sets \cite{Liu2019d,Bereyhi2020}, \emph{overlay modulation} superposes information-bearing symbols over a common auxiliary matrix \cite{Xu2020b,Zhang2021d,Hu2021b,Hua2022}, \emph{spatial modulation} switches between reflection coefficient sets that maximize \gls{snr} at different receive antennas \cite{Basar2020,Ma2020a,Yuan2021}, and \emph{index modulation} divides \gls{ris} into reflection elements for passive beamforming and information elements for on-off modulation \cite{Hu2021a}.

	% \cite{Liu2019d,Bereyhi2020}

	% How to combine backscatter modulation and passive beamforming

	Recently, \gls{ris}-empowered \gls{sr} was introduced in \cite{Xu2020b,Hua2022,Hu2021a} where independent passive beamforming and backscatter encoding were combined using advanced architectures.
	The authors of \cite{Xu2020b,Hua2022} proposed the \gls{ris} to modulate binary message over the whole phase shift matrix and the receiver to decodes from (non-coherent) primary to (coherent) backscatter link.
	In contrast, \cite{Hu2021a} divided the \gls{ris} into reflection and information elements, and evaluated the error performance of non-coherent backscatter detection.
	% Compared to existing \gls{ris}-empowered \gls{sr} that encodes and precodes independently using advanced architecture (e.g., overlay or parallel), Metascatter softly bridges and generalizes parasitic source of \gls{sr} and reflecting element of \gls{ris} via smart input design.
